Covid-19 A Spatio-Temporal Investigation.

### 2021-01-11 Notebooks/paper_covid.rmd
Update paper_covid.rmd

 With the whole world being affected by the pandemic, it's a matter of great importance that studies about the spatio-temporal aspects of the Covid-19 pandemic should be conducted, the main goal of this paper is to present methods used to identify spatial and spatio-temporal dependence in the number of infections and deaths caused by Sars-Cov-2 in different countries accordingly to time in 2020, so these techniques may be used in future or hypothetical situations where is necessary to investigate the behavior of a pathogen agent in space and time.

@@

 The cumulative number of deaths, infections and recovered cases is given by the database, but since these numbers are only available in its daily cumulative form, it was necessary to calculate monthly quantities for each one of the variables in the period of time considered in this paper between January and December 2020. The population of each country is also available in the database, so in order to better understand the spatial and the spatio-temporal effects of Covid-19 in each location, it was necessary to calculate the ratio between the number of infections, the number of recovered cases and the quantity of deaths accordingly to the population.

@@

>>>>

 With the whole world being affected by the pandemic, it's a matter of great importance that studies about the spatio-temporal aspects of the Covid-19 pandemic should be conducted, the main goal of this paper is to present methods used to identify spatial and spatio-temporal dependence in the number of infections and deaths caused by Sars-Cov-2 in different countries according to time in 2020, so these techniques may be used in future or hypothetical situations where is necessary to investigate the behavior of a pathogen agent in space and time.

@@

 The cumulative number of deaths, infections and recovered cases is given by the database, but since these numbers are only available in its daily cumulative form, it was necessary to calculate monthly quantities for each one of the variables in the period of time considered in this paper between January and December 2020. The population of each country is also available in the database, so in order to better understand the spatial and the spatio-temporal effects of Covid-19 in each location, it was necessary to calculate the ratio between the number of infections, the number of recovered cases and the quantity of deaths in the population.

@@

 In opposition to the purely spatial scan statistic, the spatio-temporal scan statistic creates cylindrical windows in three dimensions, where the height is a representation of time,
